---
title: "Misinformation ANalysis"
author: "Zhang Bohan"
date: "2025-03-06"
output: html_document
---


```{r setup}
library(dplyr)
library(readr)
library(ggplot2)


misinfo_d=read_csv("../data/life-under-lockdown-wave2-extract.csv",show_col_types=FALSE)

knowledge_levels=c(
  'Nothing at all','Not very much','A fair amount','A great deal'
)

misinfo_d=misinfo_d %>%
  mutate(
    know_facebook=know_facebook %>%
      ordered(
        levels=knowledge_levels
      )
  )
```

#Hypotheses

H1 We expect a relationship between gender and number of misinformation beliefs

H2 We expect a relationship between age and number of misinformation beliefs

H3 We expect a relationship between relying on Facebook for knowledge and number of misinformation  beliefs

#Descriptive statistics

```{r visualise-age}
misinfo_d %>%
  ggplot(
    aes(x=age)
  )+
  geom_histogram(binwidth = 5)
```

```{r visualise-gender}
misinfo_d %>%
  ggplot(
    aes(x=gender)
  )+
  geom_bar()
```

```{r visualise-facebook-knowledge}
misinfo_d %>%
  ggplot(
    aes(x=know_facebook)
  )+
  geom_bar()
```
#Findings

##Number of misinformation of beliefs versus gender

```{r visualise-beliefs}
misinfo_d %>%
  ggplot(
    aes(x=beliefs)
  )+
  geom_histogram(binwidth = 1)
```


```{r gender-beliefs-table}
misinfo_d %>%
  group_by(gender) %>%
  summarise(
    n=n(),
    M=mean(beliefs),
    Mdn=median(beliefs),
    SD=sd(beliefs)
  )

```

```{r gender-beliefs-test}
misinfo_d %>%
  filter(gender!='In another way') %>%
  t.test(
    beliefs~gender,
    data=.
  )
  
```

In the sample,men had more misinformation beliefs(M=0,73,SD=1.14)than women(M=0.61,Sd=1.05),but this was not statistically significant,t(494.31)=-1.201,p=0.230

##Number of misinformation beliefs versus age

```{r age-beliefs-visualisation}
misinfo_d %>%
  ggplot(
    aes(x=age,y=beliefs)
  )+
  geom_jitter()
```

```{r age-beliefs-correlation}
misinfo_d %>%
  cor.test(
    ~ age + beliefs,
    data= .,
    method='pearson'
  )
```

In the sample,there is a statistically significant moderate negative correlation between age and number of misinformation beliefs,r(498)=-0.24, 95% CI [-0.32, -0.16], p<0.001.

##Number of misinformation beliefs versus reliance on Facebook for knolwedge

```{r facebook-beliefs-visualisation}
misinfo_d %>%
  ggplot(
    aes(x=know_facebook,y=beliefs)
  )+
  geom_boxplot()
```

```{r facebook-beliefs-correlation}
misinfo_d %>%
  mutate(
    know_facebook=as.numeric(know_facebook)
  )%>%
  cor.test(
    ~ know_facebook + beliefs,
    data= .,
    method='spearman'
  )
```
In the sample,there is a statistically significant moderate positive correlation between relying on Facebook for knowledge about coronavirus and number of misinformation beliefs,rs(498)=0.23, p<0.001.

##Linear model
```{r linear-model}
misinfo_d %>%
  mutate(
    Female=as.numeric(gender=='Female'),
    High_Facebook=as.numeric(
      know_facebook %in% c('A fair amount','A great deal')
    )
  )%>%
  
lm(
  beliefs~age + High_Facebook,
  data=.
)%>%
summary

```
beliefs=1.22 + -0.01 * age + 0.58 * High_Facebook + -0.17*Female

Female Facebook user:beliefs=1.22-age/100+0.59-0.17
Male Facebook user:beliefs=1.22-age/100+0.59
Female Facebook non-user:beliefs=1.22-age/100-0.17
Male Facebook non-user:beliefs=1.22-age/100






